Appendix

### 2020-03-02 manuscript/appendix.Rmd
specify CDL year
cleanup caption grammar, remove trophic gridlines

```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('', col.names = NULL, caption = "CDL category definitions. See code supplement for listing of variables classified as 'ag'")
```

@@

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes in the study extent. Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}

@@

ggplot(data = dt_bar) +
  geom_rect(aes(fill = `Trophic State`, ymax = ymax, ymin = ymin, xmin = 3, xmax = 4)) +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) +
  ylab("Percent of Lakes") +
  facet_wrap(~name)

>>>>

```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag'")
```

@@

```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al. (2017) located with our study extent. Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}

@@

ggplot(data = dt_bar) +
  geom_rect(aes(fill = `Trophic State`, ymax = ymax, ymin = ymin, xmin = 3, xmax = 4)) +
  cowplot::theme_cowplot() +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) +
  ylab("Percent of Lakes") +
  facet_wrap(~name)
